```{r}
install.packages("leaflet")
```

ggplot2 map showing the latitude and longitude as points, and a leaflet map with markers on each location
# 2 Create an interactive proportional symbol map using Leaflet that shows the spatial positions of all observed frog genera in the dataset (MAP).
```{r}
library(ggplot2)
library(leaflet)

# load the dataset
frog_data <- read.csv("PE2_frog_data.csv")

# create a basic ggplot2 map
ggplot(frog_data, aes(x = Longitude, y = Latitude)) +
  geom_point() +
  theme_bw()

# create a leaflet map with markers
leaflet(frog_data) %>%
  addTiles() %>%
  addMarkers(lng = ~Longitude, lat = ~Latitude)

```

# 2.a Use the provided longitude and latitude values for each genus observed in the data to position the symbols. The longitude and latitude values must be rounded down to only 3 decimal places.
```{r}
library(ggplot2)
library(leaflet)

# load the dataset
frog_data <- read.csv("PE2_frog_data.csv")

# round the longitude and latitude values to 3 decimal places
frog_data$Longitude <- round(frog_data$Longitude, 3)
frog_data$Latitude <- round(frog_data$Latitude, 3)

# create a basic ggplot2 map with genus symbols
ggplot(frog_data, aes(x = Longitude, y = Latitude, color = Genus, shape = Genus)) +
  geom_point(size = 3) +
  theme_bw()

# create a leaflet map with markers for each genus
leaflet(frog_data) %>%
  addTiles() %>%
  addCircleMarkers(lng = ~Longitude, lat = ~Latitude, color = ~Genus, radius = 3)

```

# 2.b Provide a range selection slider to filter the number of observations in a location that is required in order for a symbol to be visible. You must allow a minimum and maximum value to be set by the slider
```{r}
library(ggplot2)
library(leaflet)
library(dplyr)
library(shiny)

# load the dataset
frog_data <- read.csv("PE2_frog_data.csv")

# round the longitude and latitude values to 3 decimal places
frog_data$Longitude <- round(frog_data$Longitude, 3)
frog_data$Latitude <- round(frog_data$Latitude, 3)

# create a range selection slider for number of observations
ui <- fluidPage(
  sliderInput(
    inputId = "obs_filter",
    label = "Number of observations required for symbol to be visible:",
    min = 1,
    max = max(frog_data %>%
                group_by(Longitude, Latitude) %>%
                summarize(n = n()) %>%
                pull(n)),
    value = 5,
    step = 1
  ),
  leafletOutput("map")
)

# create a leaflet map with markers for each genus, filtered by number of observations
server <- function(input, output) {
  output$map <- renderLeaflet({
    frog_data %>%
      group_by(Longitude, Latitude) %>%
      summarize(n = n()) %>%
      filter(n >= input$obs_filter) %>%
      select(Longitude, Latitude) %>%
      leaflet() %>%
      addTiles() %>%
      addCircleMarkers(lng = ~Longitude, lat = ~Latitude, radius = 3)
  })
}

# run the Shiny app
shinyApp(ui, server)

```

# c. Provide a checklist to filter which frog genera to display
```{r}
library(ggplot2)
library(leaflet)
library(dplyr)
library(shiny)

# load the dataset
frog_data <- read.csv("PE2_frog_data.csv")

# round the longitude and latitude values to 3 decimal places
frog_data$Longitude <- round(frog_data$Longitude, 3)
frog_data$Latitude <- round(frog_data$Latitude, 3)

# create a range selection slider for number of observations
# and a checklist for frog genera
ui <- fluidPage(
  sliderInput(
    inputId = "obs_filter",
    label = "Number of observations required for symbol to be visible:",
    min = 1,
    max = max(frog_data %>%
                group_by(Longitude, Latitude) %>%
                summarize(n = n()) %>%
                pull(n)),
    value = 5,
    step = 1
  ),
  checkboxGroupInput(
    inputId = "genus_filter",
    label = "Select which frog genera to display:",
    choices = unique(frog_data$Genus),
    selected = unique(frog_data$Genus)
  ),
  leafletOutput("map")
)

# create a leaflet map with markers for each genus, filtered by number of observations
# and frog genera
server <- function(input, output) {
  output$map <- renderLeaflet({
    frog_data %>%
      filter(Genus %in% input$genus_filter) %>%
      group_by(Longitude, Latitude) %>%
      summarize(n = n()) %>%
      filter(n >= input$obs_filter) %>%
      select(Longitude, Latitude) %>%
      leaflet() %>%
      addTiles() %>%
      addCircleMarkers(lng = ~Longitude, lat = ~Latitude, radius = 3)
  })
}

# run the Shiny app
shinyApp(ui, server)

```

