```{r}
install.packages("leaflet")
```

ggplot2 map showing the latitude and longitude as points, and a leaflet map with markers on each location
## 2 Create an interactive proportional symbol map using Leaflet that shows the spatial positions of all observed frog genera in the dataset (MAP).
```{r}
library(ggplot2)
library(leaflet)

# load the dataset
frog_data <- read.csv("PE2_frog_data.csv")

# create a basic ggplot2 map
ggplot(frog_data, aes(x = Longitude, y = Latitude)) +
  geom_point() +
  theme_bw()

# create a leaflet map with markers
leaflet(frog_data) %>%
  addTiles() %>%
  addMarkers(lng = ~Longitude, lat = ~Latitude)

```

### 2.a Use the provided longitude and latitude values for each genus observed in the data to position the symbols. The longitude and latitude values must be rounded down to only 3 decimal places.
```{r}
library(ggplot2)
library(leaflet)

# load the dataset
frog_data <- read.csv("PE2_frog_data.csv")

# round the longitude and latitude values to 3 decimal places
frog_data$Longitude <- round(frog_data$Longitude, 3)
frog_data$Latitude <- round(frog_data$Latitude, 3)

# create a basic ggplot2 map with genus symbols
ggplot(frog_data, aes(x = Longitude, y = Latitude, color = Genus, shape = Genus)) +
  geom_point(size = 3) +
  theme_bw()

# create a leaflet map with markers for each genus
leaflet(frog_data) %>%
  addTiles() %>%
  addCircleMarkers(lng = ~Longitude, lat = ~Latitude, color = ~Genus, radius = 3)

```

### 2.b Provide a range selection slider to filter the number of observations in a location that is required in order for a symbol to be visible. You must allow a minimum and maximum value to be set by the slider
```{r}
library(ggplot2)
library(leaflet)
library(dplyr)
library(shiny)

# load the dataset
frog_data <- read.csv("PE2_frog_data.csv")

# round the longitude and latitude values to 3 decimal places
frog_data$Longitude <- round(frog_data$Longitude, 3)
frog_data$Latitude <- round(frog_data$Latitude, 3)

# create a range selection slider for number of observations
ui <- fluidPage(
  sliderInput(
    inputId = "obs_filter",
    label = "Number of observations required for symbol to be visible:",
    min = 1,
    max = max(frog_data %>%
                group_by(Longitude, Latitude) %>%
                summarize(n = n()) %>%
                pull(n)),
    value = 5,
    step = 1
  ),
  leafletOutput("map")
)

# create a leaflet map with markers for each genus, filtered by number of observations
server <- function(input, output) {
  output$map <- renderLeaflet({
    frog_data %>%
      group_by(Longitude, Latitude) %>%
      summarize(n = n()) %>%
      filter(n >= input$obs_filter) %>%
      select(Longitude, Latitude) %>%
      leaflet() %>%
      addTiles() %>%
      addCircleMarkers(lng = ~Longitude, lat = ~Latitude, radius = 3)
  })
}

# run the Shiny app
shinyApp(ui, server)

```

### c. Provide a checklist to filter which frog genera to display
```{r}
library(ggplot2)
library(leaflet)
library(dplyr)
library(shiny)

# load the dataset
frog_data <- read.csv("PE2_frog_data.csv")

# round the longitude and latitude values to 3 decimal places
frog_data$Longitude <- round(frog_data$Longitude, 3)
frog_data$Latitude <- round(frog_data$Latitude, 3)

# create a range selection slider for number of observations
# and a checklist for frog genera
ui <- fluidPage(
  sliderInput(
    inputId = "obs_filter",
    label = "Number of observations required for symbol to be visible:",
    min = 1,
    max = max(frog_data %>%
                group_by(Longitude, Latitude) %>%
                summarize(n = n()) %>%
                pull(n)),
    value = 5,
    step = 1
  ),
  checkboxGroupInput(
    inputId = "genus_filter",
    label = "Select which frog genera to display:",
    choices = unique(frog_data$Genus),
    selected = unique(frog_data$Genus)
  ),
  leafletOutput("map")
)

# create a leaflet map with markers for each genus, filtered by number of observations
# and frog genera
server <- function(input, output) {
  output$map <- renderLeaflet({
    frog_data %>%
      filter(Genus %in% input$genus_filter) %>%
      group_by(Longitude, Latitude) %>%
      summarize(n = n()) %>%
      filter(n >= input$obs_filter) %>%
      select(Longitude, Latitude) %>%
      leaflet() %>%
      addTiles() %>%
      addCircleMarkers(lng = ~Longitude, lat = ~Latitude, radius = 3)
  })
}

# run the Shiny app
shinyApp(ui, server)

```

### d. Encode to each symbol’s size the number of frogs observed for a particular frog genus at that location
```{r}
library(ggplot2)
library(leaflet)
library(dplyr)
library(shiny)

# load the dataset
frog_data <- read.csv("PE2_frog_data.csv")

# round the longitude and latitude values to 3 decimal places
frog_data$Longitude <- round(frog_data$Longitude, 3)
frog_data$Latitude <- round(frog_data$Latitude, 3)

# create a range selection slider for number of observations
# and a checklist for frog genera
ui <- fluidPage(
  sliderInput(
    inputId = "obs_filter",
    label = "Number of observations required for symbol to be visible:",
    min = 1,
    max = max(frog_data %>%
                group_by(Longitude, Latitude) %>%
                summarize(n = n()) %>%
                pull(n)),
    value = 5,
    step = 1
  ),
  checkboxGroupInput(
    inputId = "genus_filter",
    label = "Select which frog genera to display:",
    choices = unique(frog_data$Genus),
    selected = unique(frog_data$Genus)
  ),
  leafletOutput("map")
)

# create a leaflet map with markers for each genus, filtered by number of observations
# and frog genera, with symbol size encoded to number of frogs observed
server <- function(input, output) {
  output$map <- renderLeaflet({
    frog_data %>%
      filter(Genus %in% input$genus_filter) %>%
      group_by(Longitude, Latitude, Genus) %>%
      summarize(n = n()) %>%
      filter(n >= input$obs_filter) %>%
      select(Longitude, Latitude, Genus, n) %>%
      leaflet() %>%
      addTiles() %>%
      #sed the sqrt function to scale the size of each symbol proportionally 
      #to the square root of the number of frogs observed, and multiplied by 5 
      #to increase the size of each symbol for better visibility.
      addCircleMarkers(lng = ~Longitude, lat = ~Latitude, 
                       radius = ~sqrt(n)*5, 
                       color = ~Genus, 
                       stroke = TRUE, 
                       fillOpacity = 0.5, 
                       weight = 1)
  })
}

# run the Shiny app
shinyApp(ui, server)

```

### e. Use a visual variable to differentiate between the frog genera Use a different color between the frog genera
```{r}
library(ggplot2)
library(leaflet)
library(dplyr)
library(shiny)

# load the dataset
frog_data <- read.csv("PE2_frog_data.csv")

# set the color palette for the frog genera
color_palette <- rainbow(length(unique(frog_data$Genus)))

# round the longitude and latitude values to 3 decimal places
frog_data$Longitude <- round(frog_data$Longitude, 3)
frog_data$Latitude <- round(frog_data$Latitude, 3)

# create a range selection slider for number of observations
# and a checklist for frog genera
ui <- fluidPage(
  sliderInput(
    inputId = "obs_filter",
    label = "Number of observations required for symbol to be visible:",
    min = 1,
    max = max(frog_data %>%
                group_by(Longitude, Latitude) %>%
                summarize(n = n()) %>%
                pull(n)),
    value = 5,
    step = 1
  ),
  checkboxGroupInput(
    inputId = "genus_filter",
    label = "Select which frog genera to display:",
    choices = unique(frog_data$Genus),
    selected = unique(frog_data$Genus)
  ),
  leafletOutput("map")
)

# create a leaflet map with markers for each genus, filtered by number of observations
# and frog genera, with color and symbol size encoded to number of frogs observed
server <- function(input, output) {
  output$map <- renderLeaflet({
    frog_data %>%
      filter(Genus %in% input$genus_filter) %>%
      group_by(Longitude, Latitude, Genus) %>%
      summarize(n = n()) %>%
      filter(n >= input$obs_filter) %>%
      select(Longitude, Latitude, Genus, n) %>%
      leaflet() %>%
      addTiles() %>%
      addCircleMarkers(lng = ~Longitude, lat = ~Latitude, 
                       radius = ~sqrt(n)*3, 
                       color = ~color_palette[match(Genus, unique(Genus))], 
                       stroke = TRUE, 
                       fillOpacity = 0.5, 
                       weight = 1)
  })
}

# run the Shiny app
shinyApp(ui, server)

```

### f. When a symbol is clicked, show a tooltip that displays the name of the frog genus and the number of observations of that genus at that location.
```{r}
library(ggplot2)
library(leaflet)
library(dplyr)
library(shiny)


# load the dataset
frog_data <- read.csv("PE2_frog_data.csv")

# set the color palette for the frog genera
color_palette <- rainbow(length(unique(frog_data$Genus)))

# round the longitude and latitude values to 3 decimal places
frog_data$Longitude <- round(frog_data$Longitude, 3)
frog_data$Latitude <- round(frog_data$Latitude, 3)

# create a range selection slider for number of observations
# and a checklist for frog genera
ui <- fluidPage(
  sliderInput(
    inputId = "obs_filter",
    label = "Number of observations required for symbol to be visible:",
    min = 1,
    max = max(frog_data %>%
                group_by(Longitude, Latitude) %>%
                summarize(n = n()) %>%
                pull(n)),
    value = 5,
    step = 1
  ),
  checkboxGroupInput(
    inputId = "genus_filter",
    label = "Select which frog genera to display:",
    choices = unique(frog_data$Genus),
    selected = unique(frog_data$Genus)
  ),
  leafletOutput("map")
)

# create a leaflet map with markers for each genus, filtered by number of observations
# and frog genera, with color and symbol size encoded to number of frogs observed
server <- function(input, output) {
  output$map <- renderLeaflet({
    frog_data %>%
      filter(Genus %in% input$genus_filter) %>%
      group_by(Longitude, Latitude, Genus) %>%
      summarize(n = n()) %>%
      filter(n >= input$obs_filter) %>%
      select(Longitude, Latitude, Genus, n) %>%
      leaflet() %>%
      addTiles() %>%
      addCircleMarkers(lng = ~Longitude, lat = ~Latitude, 
                       radius = ~sqrt(n)*3, 
                       color = ~color_palette[match(Genus, unique(Genus))], 
                       stroke = TRUE, 
                       fillOpacity = 0.5, 
                       weight = 1, 
                       label = ~paste0("Genus name: ",Genus, "\nNumber of observations: ", n), 
                       labelOptions = labelOptions(noHide = FALSE))
  })
}

# run the Shiny app
shinyApp(ui, server)


```

### Format the output into this layout:
the range slider should on the top and centre align
the checklist should on the top right conner
```{r}
library(ggplot2)
library(leaflet)
library(dplyr)
library(shiny)

# load the dataset
frog_data <- read.csv("PE2_frog_data.csv")

# set the color palette for the frog genera
color_palette <- rainbow(length(unique(frog_data$Genus)))

# round the longitude and latitude values to 3 decimal places
frog_data$Longitude <- round(frog_data$Longitude, 3)
frog_data$Latitude <- round(frog_data$Latitude, 3)

# create a range selection slider for number of observations
# and a checklist for frog genera
ui <- fluidPage(
  fluidRow(
    column(
      width = 6,
      sliderInput(
        inputId = "obs_filter",
        label = "Number of observations required for symbol to be visible:",
        min = 1,
        max = max(frog_data %>%
                    group_by(Longitude, Latitude) %>%
                    summarize(n = n()) %>%
                    pull(n)),
        value = 5,
        step = 1
      )
    ),
    column(
      width = 6,
      checkboxGroupInput(
        inputId = "genus_filter",
        label = "Select which frog genera to display:",
        choices = unique(frog_data$Genus),
        selected = unique(frog_data$Genus)
      )
    )
  ),
  leafletOutput("map")
)

# create a leaflet map with markers for each genus, filtered by number of observations
# and frog genera, with color and symbol size encoded to number of frogs observed
server <- function(input, output) {
  output$map <- renderLeaflet({
    frog_data %>%
      filter(Genus %in% input$genus_filter) %>%
      group_by(Longitude, Latitude, Genus) %>%
      summarize(n = n()) %>%
      filter(n >= input$obs_filter) %>%
      select(Longitude, Latitude, Genus, n) %>%
      leaflet() %>%
      addTiles() %>%
      addCircleMarkers(lng = ~Longitude, lat = ~Latitude, 
                       radius = ~sqrt(n)*3, 
                       color = ~color_palette[match(Genus, unique(Genus))], 
                       stroke = TRUE, 
                       fillOpacity = 0.5, 
                       weight = 1, 
                       label = ~paste0("Genus name: ",Genus, "\nNumber of observations: ", n), 
                       labelOptions = labelOptions(noHide = FALSE))
  })
}

# run the Shiny app
shinyApp(ui, server)

```


## 1. Create a visualisation using ggplot2 that shows 
count the number of observations of each frog genera based on the number of rows
and their different preferred terrain (VIS 1). 
The visualisation should display the totals for each of the frog genera. 

```{r}
library(ggplot2)

# load the data
frog_data <- read.csv("PE2_frog_data.csv")

# create the ggplot object
#  fill the bars with different colors based on 
# the Habitat column (fill = Habitat)
ggplot(frog_data, aes(x = Genus, fill = Habitat)) +
  # create a bar chart (geom_bar()) based on the Genus column,
  # use position = "dodge" to make the bars side-by-side
  geom_bar(position = "dodge") +
  # add a title and axes labels (labs())
  labs(title = "Count of Frog Genera by Preferred Terrain",
       x = "Genus",
       y = "Count") +
  # legend for the fill colors (scale_fill_discrete())
  scale_fill_discrete(name = "Preferred Terrain") +
  # use geom_text() with stat = "count" to add the 
  # count of observations on top of each bar, 
  # positioned using position_dodge(width=0.9) 
  # and adjusted vertically using vjust = -0.5.
  geom_text(stat="count", aes(label=..count..), position=position_dodge(width=0.9), vjust=-0.5)

```

## 2. (VIS 2)Create a visualisation using ggplot2
The dataset PE2_frog_data.csv has more columns
Time_Start the observation Date 
it looks like 1899/12/30 09:00:00+00
2. (VIS 2)Create a visualisation using ggplot2 that shows 
the hours in which observations occurred for each of the top four frog genera, according to previous question. 
This must clearly show the results each hour for each genus with different colours
```{r}
library(ggplot2)

# load the data
frog_data <- read.csv("PE2_frog_data.csv")

# extract the hour from the Time_Start variable
frog_data$hour <- format(as.POSIXct(frog_data$Time_Start), format="%H")

# group by Genus and hour, and count the number of observations
frog_data_counts <- frog_data %>%
    group_by(Genus, hour) %>%
    summarise(count = n())

# select the top 4 genera based on count
top_genera <- frog_data_counts %>%
    group_by(Genus) %>%
    summarise(total = sum(count)) %>%
    top_n(4)

top_genera_names <- top_genera$Genus

# filter the frog_data_counts to only include the top 4 genera
frog_data_counts_top <- frog_data_counts %>%
    filter(Genus %in% top_genera_names)

# create the ggplot object
ggplot(frog_data_counts_top, aes(x = hour, y = count, fill = Genus)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = "Observation Hours for Top 4 Frog Genera",
         x = "Hour of Day",
         y = "Count",
         fill = "Genus") +
    scale_fill_brewer(palette="Set1") +
    theme_minimal()

```

```{r}
library(ggplot2)
library(dplyr)

# load the data
frog_data <- read.csv("PE2_frog_data.csv")

# extract the hour from the Time_Start variable
frog_data$hour <- format(as.POSIXct(frog_data$Time_Start), format="%H")

# group by Genus and hour, and count the number of observations
#  .groups = "drop" to the summarise() function call ensures that the output is ungrouped
frog_data_counts <- frog_data %>%
  group_by(Genus, hour) %>%
  summarise(count = n(), .groups = "drop")

# select the top 4 genera based on count
top_genera <- frog_data_counts %>%
  group_by(Genus) %>%
  summarise(total = sum(count)) %>%
  top_n(4)

top_genera_names <- top_genera$Genus

# filter the frog_data_counts to only include the top 4 genera
frog_data_counts_top <- frog_data_counts %>%
  filter(Genus %in% top_genera_names)

# create the ggplot object
ggplot(frog_data_counts_top, aes(x = hour, y = count, fill = Genus)) +
  #  geom_bar() to create a bar chart of counts for each hour and genus
  #  position = "dodge" to make the bars side-by-side
  geom_bar(stat = "identity", position = "dodge") +
  #  add a title and axes labels using labs()
  labs(title = "Observation Hours for Top 4 Frog Genera",
       x = "Hour of Day",
       y = "Count",
       fill = "Genus") +
  # fill legend using scale_fill_brewer() with a Set1 color palette.
  scale_fill_brewer(palette="Set1") +
  # use the theme_minimal() function from the ggplot2 package to simplify the appearance of the plot.
  theme_minimal()

```

# Compose VIS1, VIS2, MAP, and DES1, DES2, DES3 layout
DES1	text block about project description
DES2 	text block about frog frequency and location description
DES3	text block about VIS2 description
into a nice looking layout using Shiny (preferably using a fixed layout, instead of fluid layout). 
On the top of the page is the title "FROGS Observation",
below the title is DES1,
below DES1 is VIS1 and MAP with same height. VIS1 on the left and MAP on the right,
below VIS1 and MAP is DES2,
Below DES2 is DES3 and VIS2 with same height. DES3 on the left and VIS2 on the right,
```{r}
library(shiny)
library(ggplot2)
library(leaflet)
library(dplyr)

# load the dataset
frog_data <- read.csv("PE2_frog_data.csv")

# set the color palette for the frog genera
color_palette <- rainbow(length(unique(frog_data$Genus)))

# round the longitude and latitude values to 3 decimal places
frog_data$Longitude <- round(frog_data$Longitude, 3)
frog_data$Latitude <- round(frog_data$Latitude, 3)

# create a range selection slider for number of observations
# and a checklist for frog genera
ui <- fluidPage(
  
  # Page title
  fluidRow(
    column(12,
           h1("FROGS Observation"))),
  
  # Project description
  fluidRow(
    column(12,
           h4("Project Description")),
    column(12,
           p("{{DES1}}"))
  ),
  
  # Main content
  fluidRow(
    # VIS1 and MAP
    column(6,
           h4("Count of Frog Genera and Observation Points")),
    column(6,
           h4("Map of Observation Locations")),
    fluidRow(
      column(6,
             plotOutput("vis1_plot")),
      column(6,
             leafletOutput("map"))
    ),
    
    # DES2
    column(12,
           h4("Frog Frequency and Location Description")),
    column(12,
           p("{{DES2}}")),
    
    # VIS2 and DES3
    column(6,
           h4("Observation Hours for Top 4 Frog Genera")),
    column(6,
           h4("{{DES3}}")),
    fluidRow(
      column(6,
             plotOutput("vis2_plot")),
      column(6,
             p("{{DES4}}"))
    )
  )
)

# server logic
server <- function(input, output) {
  
  # VIS1 bar chart
  output$vis1_plot <- renderPlot({
    ggplot(frog_data, aes(x = Genus, fill = Habitat)) +
      geom_bar(position = "dodge") +
      labs(title = "Count of Frog Genera by Preferred Terrain",
           x = "Genus",
           y = "Count") +
      scale_fill_discrete(name = "Preferred Terrain") +
      geom_text(stat="count", aes(label=..count..), position=position_dodge(width=0.9), vjust=-0.5)
  })
  
  # MAP leaflet map
  output$map <- renderLeaflet({
    frog_data %>%
      filter(Genus %in% input$genus_filter) %>%
      group_by(Longitude, Latitude, Genus) %>%
      summarize(n = n()) %>%
      filter(n >= input$obs_filter) %>%
      select(Longitude, Latitude, Genus, n) %>%
      leaflet() %>%
      addTiles() %>%
      addCircleMarkers(lng = ~Longitude, lat = ~Latitude, 
                       radius = ~sqrt(n)*3, 
                       color = ~color_palette[match(Genus, unique(Genus))], 
                       stroke = TRUE, 
                       fillOpacity = 0.5, 
                       weight = 1, 
                       label = ~paste0("Genus name: ",Genus, "\nNumber of observations: ", n), 
                       labelOptions = labelOptions(noHide = FALSE))
  })
  
  # VIS2 bar chart
  output$vis2_plot <- renderPlot({
    frog_data_counts <- frog_data %>%
      group_by(Genus, hour) %>%
      summarise(count = n(), .groups = "drop")
    
    top_genera <- frog_data_counts %>%
      group_by(Genus) %>%
      summarise(total = sum(count)) %>%
      top_n(n = 4, wt = total)
    
    top_genera_names <- top_genera$Genus
    
    frog_data_counts_top <- frog_data_counts %>%
      filter(Genus %in% top_genera_names)
    
    ggplot(frog_data_counts_top, aes(x = hour, y = count, fill = Genus)) +
      geom_bar(stat = "identity", position = "dodge") +
      labs(title = "Observation Hours for Top 4 Frog Genera",
           x = "Hour of Day",
           y = "Count",
           fill = "Genus") +
      scale_fill_brewer(palette="Set1") +
      theme_minimal()
  })
}

# shiny app and server
shinyApp(ui = ui, server = server)


```

```{r}
# Define the UI for the Shiny app
ui <- fluidPage(
  
  # Set the app title
  titlePanel("FROGS Observation"),
  
  # Set the fixed layout with a sidebar and a main panel
  fixedRow(
    column(
      width = 4,
      # Add the DES1 section
      wellPanel(
        h4("Description 1"),
        p("This app shows the observation data of frogs in a certain area, 
           and allows filtering based on the number of observations and frog genera.")
      )
    ),
    column(
      width = 8,
      # Add the VIS1 and MAP sections side-by-side
      fluidRow(
        column(
          width = 6,
          wellPanel(
            # Add the VIS1 section
            h4("Distribution of Observation Time"),
            plotOutput("vis1", height = "350px")
          )
        ),
        column(
          width = 6,
          wellPanel(
            # Add the MAP section
            h4("Geographic Distribution of Observations"),
            leafletOutput("map", height = "350px")
          )
        )
      )
    )
  ),
  
  fixedRow(
    column(
      width = 4,
      # Add the DES2 section
      wellPanel(
        h4("Description 2"),
        p("The map shows the geographic distribution of observations for selected frog genera, 
           with the symbol size and color representing the number of observations.")
      )
    ),
    column(
      width = 8,
      # Add the VIS2 section
      wellPanel(
        h4("Observation Hours for Top 4 Frog Genera"),
        plotOutput("vis2", height = "350px")
      )
    )
  ),
  
  # Add the DES3 section
  wellPanel(
    h4("Description 3"),
    p("The bar chart shows the distribution of observation times for the top 4 frog genera 
       based on the number of observations.")
  )
  
)

server <- function(input, output) {
  # load the dataset
  frog_data <- read.csv("PE2_frog_data.csv")
  
  # set the color palette for the frog genera
  color_palette <- rainbow(length(unique(frog_data$Genus)))
  
  # round the longitude and latitude values to 3 decimal places
  frog_data$Longitude <- round(frog_data$Longitude, 3)
  frog_data$Latitude <- round(frog_data$Latitude, 3)
  
  # filter the frog_data_counts to only include the top 4 genera
  frog_data_counts_top <- frog_data %>%
    group_by(Genus, hour) %>%
    summarise(count = n(), .groups = "drop") %>%
    group_by(Genus) %>%
    summarise(total = sum(count)) %>%
    top_n(4) %>%
    inner_join(frog_data_counts, by = "Genus") %>%
    filter(Genus %in% top_genera_names)
  
  # render the text output for DES1
  output$des1 <- renderText({
    "This dashboard shows observations of different frog genera and their habitats. The observations were made by researchers during their fieldwork. Use the filters and interactive maps to explore the data."
  })
  
  # render the leaflet map for MAP
  output$map <- renderLeaflet({
    frog_data %>%
      filter(Genus %in% input$genus_filter) %>%
      group_by(Longitude, Latitude, Genus) %>%
      summarize(n = n()) %>%
      filter(n >= input$obs_filter) %>%
      select(Longitude, Latitude, Genus, n) %>%
      leaflet() %>%
      addTiles() %>%
      addCircleMarkers(lng = ~Longitude, lat = ~Latitude, 
                       radius = ~sqrt(n)*3, 
                       color = ~color_palette[match(Genus, unique(Genus))], 
                       stroke = TRUE, 
                       fillOpacity = 0.5, 
                       weight = 1, 
                       label = ~paste0("Genus name: ",Genus, "\nNumber of observations: ", n), 
                       labelOptions = labelOptions(noHide = FALSE))
  })
  
  # render the bar chart for VIS1
  output$vis1 <- renderPlot({
    # use the same code block as in VIS1
    ggplot(frog_data_counts_top, aes(x = hour, y = count, fill = Genus)) +
      geom_bar(stat = "identity", position = "dodge") +
      labs(title = "Observation Hours for Top 4 Frog Genera",
           x = "Hour of Day",
           y = "Count",
           fill = "Genus") +
      scale_fill_brewer(palette="Set1") +
      theme_minimal()
  })
  
  # render the text output for DES2
  output$des2 <- renderText({
    "The map on the right shows the locations of the frog observations. You can filter by the number of observations required for a frog genus to appear and select which genera to display. Hover over a marker to see the genus name and number of observations."
  })
  
  # render the bar chart for VIS2
  output$vis2 <- renderPlot({
    # use the same code block as in VIS2
    ggplot(frog_data_counts_top, aes(x = hour, y = count, fill = Genus)) +
      geom_bar(stat = "identity", position = "dodge") +
      labs(title = "Observation Hours for Top 4 Frog Genera",
           x = "Hour of Day",
           y = "Count",
           fill = "Genus") +
      scale_fill_brewer(palette="Set1") +
      theme_minimal()
  })
  
  # render the text output for DES3
  output$des3 <- renderText({
    "The bar chart on the left shows the number of observations of the top 4 frog genera by hour of the day. Use the filter on the top of the page to select which genera to display. The chart shows that most observations were made during the early morning and late evening hours."
  })
  
}


# Run the Shiny app
shinyApp(ui, server)

```

