```{r}
install.packages("openxlsx")

```

```{r}
install.packages("reshape2")

```

# Where does the majority of the game happen
```{r}
library(tidyverse)
library(readxl)

# Load the files into dataframes
combined_pass <- read_excel("data_clean/combined_Pass.xlsx")
combined_attack <- read_excel("data_clean/combined_attack.xlsx")

# Select the relevant columns and rename them
pass_data <- combined_pass %>%
  select(Touch_Defend, Touch_Middle, Touch_Attck) %>%
  rename("Defensive Third" = Touch_Defend,
         "Middle Third" = Touch_Middle,
         "Final Third" = Touch_Attck)

attack_data <- combined_attack %>%
  select(Attack_Left, Attack_middle, Attack_right) %>%
  rename("Left side" = Attack_Left,
         "Middle side" = Attack_middle,
         "Right side" = Attack_right)

# Calculate the sum of each column
pass_sum <- pass_data %>% summarise(across(everything(), sum))
attack_sum <- attack_data %>% summarise(across(everything(), sum))

# Reshape the data for plotting
pass_sum <- pass_sum %>% pivot_longer(cols = everything(), names_to = "Location", values_to = "Touches")
attack_sum <- attack_sum %>% pivot_longer(cols = everything(), names_to = "Location", values_to = "Attacks")

# Create a bar chart for the pass data
pass_plot <- ggplot(pass_sum, aes(x = Location, y = Touches, fill = Location)) +
             geom_bar(stat = "identity") +
             labs(title = "Total Passes average per game by Location", y = "Total Passes", x = "Location") +
             scale_fill_brewer(palette = "Paired")

# Create a bar chart for the attack data
attack_plot <- ggplot(attack_sum, aes(x = Location, y = Attacks, fill = Location)) +
               geom_bar(stat = "identity") +
               labs(title = "Total Attacks pass average per game  by Location", y = "Total Attacks", x = "Location") +
               scale_fill_brewer(palette = "Paired")

# Display the plots
print(pass_plot)
print(attack_plot)

ggsave("data_plot/pass_plot.png", plot = pass_plot, width = 6, height = 4)
ggsave("data_plot/attack_plot.png", plot = attack_plot, width = 6, height = 4)

```
#  which area is most dangerous for the defense?
# by angle
```{r}
# Load libraries
library(openxlsx)
library(ggplot2)

# Read data
attack_data <- read.xlsx("data_clean/combined_attack.xlsx", sheet = 1, startRow = 1)

# Calculate average values
avg_left <- mean(attack_data$Shot_left)
avg_middle <- mean(attack_data$Shot_middle)
avg_right <- mean(attack_data$Shot_right)

# Create a data frame for plotting
avg_df <- data.frame(location = c("Left", "Middle", "Right"), 
                     average = c(avg_left, avg_middle, avg_right))

# Create the plot
shot_angle <- ggplot(data = avg_df, aes(x = location, y = average, fill = location)) +
  geom_bar(stat = "identity", color = "black", alpha = .8) +
  ggtitle("Average Shots Taken of all teams by Angle") +
  xlab("Shot Location") +
  ylab("Average Shots per game") +
  theme_minimal() +
  theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
        axis.title = element_text(size = 14, face = "bold"),
        axis.text = element_text(size = 12),
        legend.position = "none") +
  geom_text(aes(label = round(average, 2)), vjust = -0.5, size = 4)

print(shot_angle)
ggsave("data_plot/shot_angle.png", plot = shot_angle, width = 6, height = 4)
```

#  which area is most dangerous for the defense?
# by range
```{r}
# Load libraries
library(openxlsx)
library(ggplot2)

# Read data
attack_data <- read.xlsx("data_clean/combined_attack.xlsx", sheet = 1, startRow = 1)

# Calculate average values
avg_left <- mean(attack_data$Shot_in_6_yard_box)
avg_middle <- mean(attack_data$Shot_in_18_yard_box)
avg_right <- mean(attack_data$Shot_outsie_box)

# Create a data frame for plotting
avg_df <- data.frame(location = c("Goal", "Penalty", "Out of Box"), 
                     average = c(avg_left, avg_middle, avg_right))

# Create the plot
shot_range <- ggplot(data = avg_df, aes(x = location, y = average, fill = location)) +
  geom_bar(stat = "identity", color = "black", alpha = .8) +
  ggtitle("Average Shots Taken of all teams by Location") +
  xlab("Shot Location") +
  ylab("Average Shots per game") +
  theme_minimal() +
  theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
        axis.title = element_text(size = 14, face = "bold"),
        axis.text = element_text(size = 12),
        legend.position = "none") +
  geom_text(aes(label = round(average, 2)), vjust = -0.5, size = 4)

print(shot_range)
ggsave("data_plot/shot_range.png", plot = shot_range, width = 6, height = 4)
```


```{r}
# Load libraries
library(openxlsx)
library(ggplot2)

# Read data
attack_data <- read.xlsx("data_clean/combined_attack.xlsx", sheet = 1, startRow = 1)

# Calculate average values
avg_left <- mean(attack_data$Shot_in_6_yard_box)
avg_middle <- mean(attack_data$Shot_in_18_yard_box)
avg_right <- mean(attack_data$Shot_outsie_box)

# Create a data frame for plotting
avg_df <- data.frame(location = c("Goal", "Penalty", "Out of Box"), 
                     average = c(avg_left, avg_middle, avg_right))

# Create the plot
ggplot(data = avg_df, aes(x = "", y = average, fill = location)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar(theta = "y") +
  ggtitle("Average Shots Taken of all teams by Location") +
  xlab("") +
  ylab("") +
  theme_void() +
  theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
        axis.title = element_blank(),
        axis.text = element_blank(),
        legend.position = c(0.85, 0.85),
        legend.title = element_blank(),
        panel.grid = element_blank()) +
  scale_fill_brewer(palette = "Set1")


```

# Which match statistics (like pass completion rates, successful dribbles, and interceptions) does Croatia Team do better than other
# from attck
# search all columns from combined_attack.xlsx in Croatia row. compare the value with the average. put the value larger than average in positive and lower than average value columns in negative.
```{r}
# Load libraries
library(openxlsx)
library(ggplot2)

# Read data for Combined Attack
attack_data <- read.xlsx("data_clean/combined_attack.xlsx", sheet = 1, startRow = 1)

# Find Croatia's row
croatia_row <- attack_data[attack_data$Team == "Croatia", ]

# Calculate average values
avg_values <- colMeans(attack_data[, -1])

# Calculate differences between Croatia's values and averages
differences <- croatia_row[, -1] - avg_values

# Create a named vector of values
diff_vector <- setNames(differences, colnames(attack_data[, -1]))

# Calculate the percentage difference
percentage_diff <- round((differences / avg_values) * 100, 1)

# Create a named vector of values
diff_vector <- setNames(percentage_diff , colnames(attack_data[, -1]))



# Create a data frame for plotting
diff_df <- data.frame(statistic = names(diff_vector),
                      difference = as.numeric(diff_vector))

# Create the plot
Croatia_attack <- ggplot(data = diff_df, aes(x = statistic, y = difference, fill = difference > 0)) +
  geom_bar(stat = "identity", color = "black") +
  scale_fill_manual(values = c("red", "green"), name = "Difference") +
  geom_hline(yintercept = 0, color = "black", size = 1) +
  ggtitle("Croatia's Attack Statistics to the Average percentage") +
  xlab("") +
  ylab("Difference from Average (%)") +
  theme_minimal() +
  theme(plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_text(size = 6),
        axis.text.y = element_text(size = 6),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(colour = "grey", linetype = "dashed", size = 0.5),
        panel.background = element_rect(fill = "white"),
        panel.border = element_rect(fill = NA, colour = "black", size = 1),
        plot.background = element_rect(fill = "#F0F0F0"),
        plot.margin = unit(c(1, 2, 1, 1), "mm")) +
  coord_flip() +
  labs(fill = "Difference")


print(Croatia_attack)
ggsave("data_plot/Croatia_attack.png", plot = Croatia_attack, width = 6, height = 4)
```

# from Defend
# search all columns from combined_Defend.xlsx in Croatia row. compare the value with the average. put the value larger than average in positive and lower than average value columns in negative.
```{r}
# Load libraries
library(openxlsx)
library(ggplot2)

# Read data for Combined Attack
attack_data <- read.xlsx("data_clean/combined_Defend.xlsx", sheet = 1, startRow = 1)

# Find Croatia's row
croatia_row <- attack_data[attack_data$Team == "Croatia", ]

# Calculate average values
avg_values <- colMeans(attack_data[, -1])

# Calculate differences between Croatia's values and averages
differences <- croatia_row[, -1] - avg_values

# Create a named vector of values
diff_vector <- setNames(differences, colnames(attack_data[, -1]))

# Calculate the percentage difference
percentage_diff <- round((differences / avg_values) * 100, 1)

# Create a named vector of values
diff_vector <- setNames(percentage_diff , colnames(attack_data[, -1]))

# Create a data frame for plotting
diff_df <- data.frame(statistic = names(diff_vector),
                      difference = as.numeric(diff_vector))

# Create the plot
Croatia_defend <- ggplot(data = diff_df, aes(x = statistic, y = difference, fill = difference > 0)) +
  geom_bar(stat = "identity", color = "black") +
  scale_fill_manual(values = c("red", "green"), name = "Difference") +
  geom_hline(yintercept = 0, color = "black", size = 1) +
  ggtitle("Croatia's Defend Statistics to the Average percentage") +
  xlab("") +
  ylab("Difference from Average (%)") +
  theme_minimal() +
  theme(plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_text(size = 6),
        axis.text.y = element_text(size = 6),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(colour = "grey", linetype = "dashed", size = 0.5),
        panel.background = element_rect(fill = "white"),
        panel.border = element_rect(fill = NA, colour = "black", size = 1),
        plot.background = element_rect(fill = "#F0F0F0"),
        plot.margin = unit(c(1, 2, 1, 1), "mm")) +
  coord_flip() +
  labs(fill = "Difference")


print(Croatia_defend)
ggsave("data_plot/Croatia_defend.png", plot = Croatia_defend, width = 6, height = 4)
```




# from Pass
# search all columns from combined_Pass.xlsx in Croatia row. compare the value with the average. put the value larger than average in positive and lower than average value columns in negative.
```{r}
# Load libraries
library(openxlsx)
library(ggplot2)

# Read data for Combined Attack
attack_data <- read.xlsx("data_clean/combined_Pass.xlsx", sheet = 1, startRow = 1)

# Find Croatia's row
croatia_row <- attack_data[attack_data$Team == "Croatia", ][, -1]

# Calculate average values
avg_values <- colMeans(attack_data[, -1])

# Calculate differences between Croatia's values and averages
differences <- croatia_row - avg_values

# Create a named vector of values
diff_vector <- setNames(differences, colnames(attack_data[, -1]))

# Calculate the percentage difference
percentage_diff <- round((differences / avg_values) * 100, 1)

# Create a named vector of values
diff_vector <- setNames(percentage_diff , colnames(attack_data[, -1]))

# Create a data frame for plotting
diff_df <- data.frame(statistic = names(diff_vector),
                      difference = as.numeric(diff_vector))

# Create the plot
Croatia_pass <- ggplot(data = diff_df, aes(x = statistic, y = difference, fill = difference > 0)) +
  geom_bar(stat = "identity", color = "black") +
  scale_fill_manual(values = c("red", "green"), name = "Difference") +
  geom_hline(yintercept = 0, color = "black", size = 1) +
  ggtitle("Croatia's Pass Statistics to the Average percentage") +
  xlab("") +
  ylab("Difference from Average (%)") +
  theme_minimal() +
  theme(plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_text(size = 6),
        axis.text.y = element_text(size = 6),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(colour = "grey", linetype = "dashed", size = 0.5),
        panel.background = element_rect(fill = "white"),
        panel.border = element_rect(fill = NA, colour = "black", size = 1),
        plot.background = element_rect(fill = "#F0F0F0"),
        plot.margin = unit(c(1, 2, 1, 1), "mm")) +
  coord_flip() +
  labs(fill = "Difference")

print(Croatia_pass)
ggsave("data_plot/Croatia_pass.png", plot = Croatia_pass, width = 6, height = 4)

```
.

# Which match statistics (like pass completion rates, successful dribbles, and interceptions) does Belgium Team do better than other
# from attck
# search all columns from combined_attack.xlsx in Belgium row. compare the value with the average. put the value larger than average in positive and lower than average value columns in negative.
```{r}
# Load libraries
library(openxlsx)
library(ggplot2)

# Read data for Combined Attack
attack_data <- read.xlsx("data_clean/combined_attack.xlsx", sheet = 1, startRow = 1)

# Find Croatia's row
croatia_row <- attack_data[attack_data$Team == "Belgium", ]

# Calculate average values
avg_values <- colMeans(attack_data[, -1])

# Calculate differences between Croatia's values and averages
differences <- croatia_row[, -1] - avg_values

# Create a named vector of values
diff_vector <- setNames(differences, colnames(attack_data[, -1]))

# Calculate the percentage difference
percentage_diff <- round((differences / avg_values) * 100, 1)

# Create a named vector of values
diff_vector <- setNames(percentage_diff , colnames(attack_data[, -1]))



# Create a data frame for plotting
diff_df <- data.frame(statistic = names(diff_vector),
                      difference = as.numeric(diff_vector))

# Create the plot
Belgium_attack <- ggplot(data = diff_df, aes(x = statistic, y = difference, fill = difference > 0)) +
  geom_bar(stat = "identity", color = "black") +
  scale_fill_manual(values = c("red", "green"), name = "Difference") +
  geom_hline(yintercept = 0, color = "black", size = 1) +
  ggtitle("Belgium's Attack Statistics to the Average percentage") +
  xlab("") +
  ylab("Difference from Average (%)") +
  theme_minimal() +
  theme(plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_text(size = 6),
        axis.text.y = element_text(size = 6),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(colour = "grey", linetype = "dashed", size = 0.5),
        panel.background = element_rect(fill = "white"),
        panel.border = element_rect(fill = NA, colour = "black", size = 1),
        plot.background = element_rect(fill = "#F0F0F0"),
        plot.margin = unit(c(1, 2, 1, 1), "mm")) +
  coord_flip() +
  labs(fill = "Difference")


print(Belgium_attack)
ggsave("data_plot/Belgium_attack.png", plot = Belgium_attack, width = 6, height = 4)
```

# from Defend
# search all columns from combined_Defend.xlsx in Croatia row. compare the value with the average. put the value larger than average in positive and lower than average value columns in negative.
```{r}
# Load libraries
library(openxlsx)
library(ggplot2)

# Read data for Combined Attack
attack_data <- read.xlsx("data_clean/combined_Defend.xlsx", sheet = 1, startRow = 1)

# Find Croatia's row
croatia_row <- attack_data[attack_data$Team == "Belgium", ]

# Calculate average values
avg_values <- colMeans(attack_data[, -1])

# Calculate differences between Croatia's values and averages
differences <- croatia_row[, -1] - avg_values

# Create a named vector of values
diff_vector <- setNames(differences, colnames(attack_data[, -1]))

# Calculate the percentage difference
percentage_diff <- round((differences / avg_values) * 100, 1)

# Create a named vector of values
diff_vector <- setNames(percentage_diff , colnames(attack_data[, -1]))

# Create a data frame for plotting
diff_df <- data.frame(statistic = names(diff_vector),
                      difference = as.numeric(diff_vector))

# Create the plot
Belgium_defend <- ggplot(data = diff_df, aes(x = statistic, y = difference, fill = difference > 0)) +
  geom_bar(stat = "identity", color = "black") +
  scale_fill_manual(values = c("red", "green"), name = "Difference") +
  geom_hline(yintercept = 0, color = "black", size = 1) +
  ggtitle("Belgium's Defend Statistics to the Average percentage") +
  xlab("") +
  ylab("Difference from Average (%)") +
  theme_minimal() +
  theme(plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_text(size = 6),
        axis.text.y = element_text(size = 6),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(colour = "grey", linetype = "dashed", size = 0.5),
        panel.background = element_rect(fill = "white"),
        panel.border = element_rect(fill = NA, colour = "black", size = 1),
        plot.background = element_rect(fill = "#F0F0F0"),
        plot.margin = unit(c(1, 2, 1, 1), "mm")) +
  coord_flip() +
  labs(fill = "Difference")


print(Belgium_defend)
ggsave("data_plot/Belgium_defend.png", plot = Belgium_defend, width = 6, height = 4)
```


# from Pass
# search all columns from combined_Pass.xlsx in Belgium row. compare the value with the average. put the value larger than average in positive and lower than average value columns in negative.
```{r}
# Load libraries
library(openxlsx)
library(ggplot2)

# Read data for Combined Attack
attack_data <- read.xlsx("data_clean/combined_Pass.xlsx", sheet = 1, startRow = 1)

# Find Croatia's row
croatia_row <- attack_data[attack_data$Team == "Belgium", ][, -1]

# Calculate average values
avg_values <- colMeans(attack_data[, -1])

# Calculate differences between Croatia's values and averages
differences <- croatia_row - avg_values

# Create a named vector of values
diff_vector <- setNames(differences, colnames(attack_data[, -1]))

# Calculate the percentage difference
percentage_diff <- round((differences / avg_values) * 100, 1)

# Create a named vector of values
diff_vector <- setNames(percentage_diff , colnames(attack_data[, -1]))

# Create a data frame for plotting
diff_df <- data.frame(statistic = names(diff_vector),
                      difference = as.numeric(diff_vector))

# Create the plot
Belgium_pass <- ggplot(data = diff_df, aes(x = statistic, y = difference, fill = difference > 0)) +
  geom_bar(stat = "identity", color = "black") +
  scale_fill_manual(values = c("red", "green"), name = "Difference") +
  geom_hline(yintercept = 0, color = "black", size = 1) +
  ggtitle("Belgium's Pass Statistics to the Average percentage") +
  xlab("") +
  ylab("Difference from Average (%)") +
  theme_minimal() +
  theme(plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_text(size = 6),
        axis.text.y = element_text(size = 6),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(colour = "grey", linetype = "dashed", size = 0.5),
        panel.background = element_rect(fill = "white"),
        panel.border = element_rect(fill = NA, colour = "black", size = 1),
        plot.background = element_rect(fill = "#F0F0F0"),
        plot.margin = unit(c(1, 2, 1, 1), "mm")) +
  coord_flip() +
  labs(fill = "Difference")


print(Belgium_pass)
ggsave("data_plot/Belgium_pass.png", plot = Belgium_pass, width = 6, height = 4)
```




#  Did teams who scored more goals have a higher chance of winning the tournament? 
```{r}
# Load libraries
library(openxlsx)
library(dplyr)
library(ggplot2)

# Read team_data.xlsx file
team_data <- read.xlsx("data_clean/team_data.xlsx", sheet = 1, startRow = 1)

# Filter the data frame to select only columns games, goals_per90, and xg_per90
team_data_filtered <- select(team_data, games, goals_per90, xg_per90)

# Group the data frame by games and summarize the mean of goals_per90 and xg_per90 for each group
team_data_summary <- group_by(team_data_filtered, games) %>%
  summarize(mean_goals_per90 = mean(goals_per90),
            mean_xg_per90 = mean(xg_per90))

# Create the plot
ggplot(team_data_summary, aes(x = games, y = mean_goals_per90, group = 1)) +
  geom_line(color = "red", size = 1.5) +
  geom_line(aes(y = mean_xg_per90), color = "blue", size = 1.5) +
  ggtitle("Goals per 90 vs xG per 90 based on games") +
  xlab("Number of Games Played") +
  ylab("Mean Goals per 90 / xG per 90") +
  theme_minimal() +
  theme(plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10),
        legend.title = element_blank(),
        legend.text = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.border = element_rect(fill = NA, colour = "black", size = 1),
        plot.background = element_rect(fill = "#F0F0F0"),
        plot.margin = unit(c(1, 1, 1, 1), "cm"))

# Save the plot
ggsave("data_plot/goals_vs_xg.png", type = "cairo", dpi = 300, width = 6, height = 4, units = "in")

```
another version
```{r}
# Load libraries
library(openxlsx)
library(dplyr)
library(ggplot2)

# Read the team data
team_data <- read.xlsx("data_clean/team_data.xlsx", sheet = 1)

# Select games, goals per 90, and xg per 90 columns
selected_cols <- team_data %>% select(games, goals_per90, xg_per90)

# Calculate the average goals_per90 and xg_per90 for each value of games
avg_vals <- selected_cols %>% group_by(games) %>% summarize(avg_goals_per90 = mean(goals_per90, na.rm = TRUE), avg_xg_per90 = mean(xg_per90, na.rm = TRUE)) 

# Create a plot of avg_goals_per90 and avg_xg_per90 for each value of games
ggplot(avg_vals, aes(x = games, y = avg_goals_per90, group = 1)) + 
  geom_line(color = "blue") + 
  geom_point(size = 2, color = "blue") +
  geom_line(aes(y = avg_xg_per90), color = "red") +
  geom_point(aes(y = avg_xg_per90), size = 2, color = "red") +
  labs(x = "Games", y = "Per 90 Average", title = "Per 90 averages for games played") + 
  scale_x_continuous(breaks = seq(0, max(avg_vals$games), by = 2)) +
  scale_y_continuous(limits = c(0, max(max(avg_vals$avg_goals_per90), max(avg_vals$avg_xg_per90))) * 1.1) + 
  theme_classic()

```
third version
```{r}
# Load libraries
library(openxlsx)
library(dplyr)
library(ggplot2)

# Read the team data
team_data <- read.xlsx("data_clean/team_data.xlsx", sheet = 1)

# Select team, games, goals per 90, and xg per 90 columns
selected_cols <- team_data %>% select(team, games, goals_per90, xg_per90)

# Filter the rows where games = 3
filtered_data <- selected_cols %>% filter(games == 3)

# Select the team, goals per 90, and xg per 90 columns
plot_data <- filtered_data %>% select(team, goals_per90, xg_per90)

# Create a plot of goals_per90 and xg_per90 for each team
ggplot(plot_data, aes(x = goals_per90, y = xg_per90, label = team)) + 
  geom_point() + 
  geom_text() +
  labs(x = "Goals per 90", y = "xG per 90", title = "Goals per 90 vs xG per 90 for 3 games played") + 
  theme_classic()

```
fourth version
```{r}
# Load libraries
library(openxlsx)
library(dplyr)
library(ggplot2)

# Read the team data
team_data <- read.xlsx("data_clean/team_data.xlsx", sheet = 1)

# Select team, games, goals per 90, and xg per 90 columns
selected_cols <- team_data %>% select(team, games, goals_per90, xg_per90)

# Filter the rows where games = 3, 4, 5, and 7
filtered_data <- selected_cols %>%
  filter(games %in% c(3, 4, 5, 7))

# Select the team, goals per 90, and xg per 90 columns
plot_data <- filtered_data %>% select(team, games, goals_per90, xg_per90)

# Create a plot of goals_per90 and xg_per90 for each team
ggplot(plot_data, aes(x = goals_per90, y = xg_per90, label = team, col = as.factor(games))) + 
  geom_point(size = 3) + 
  geom_text(size = 3, nudge_x = 0.2, nudge_y = 0.2) + 
  labs(x = "goals per game", y = "Expected goals per game", title = "Goals and Expected per game") +
  labs(col="Match")+
  scale_color_manual(values = c("#00FF00", "#808080", "#FF0000", "#0000FF"),
                     breaks = c(3, 4, 5, 7), 
                     labels = c("3 games", "4 games", "5 games", "7 games")) +
  theme_classic()


# Save the plot
ggsave("data_plot/goals_vs_xg.png", type = "cairo", dpi = 300, width = 6, height = 4, units = "in")
```


# which factors take the matter with scored?

# detect if two columns have linear realtion
```{r}
# Load libraries
library(openxlsx)
library(ggplot2)
library(tidyverse)
library(reshape2)

# Read the XLSX file
data <- read.xlsx("data_clean/team_data.xlsx")

# Select the two columns you want to analyze
selected_cols <- data[, c("shots_per90", "shots_on_target_per90", "shots_free_kicks","gk_pens_allowed", "corner_kicks","errors", "goals")]

ggplot(melt(selected_cols, id.vars = "goals"), aes(x = value, y = goals)) +
  geom_point() +
  facet_grid(variable ~ ., scales = "free") +
  labs(title = "Linear Regression Analysis of goals per90") +
  theme_bw()

```

```{r}
# Load libraries
library(openxlsx)
library(ggplot2)
library(tidyverse)
library(reshape2)

# Read the XLSX file
data <- read.xlsx("data_clean/team_data.xlsx")

# Select the two columns you want to analyze
selected_cols <- data[, c("shots_per90", "shots_on_target_per90", "shots_free_kicks", "gk_pens_allowed", "corner_kicks","sca_passes_dead", "goals_per90")]

# Create a scatter plot for each column
ggplot(melt(selected_cols, id.vars = "goals_per90"), aes(x = value, y = goals_per90)) +
  geom_point() +
  facet_wrap(~ variable, scales = "free") +
  labs(x = "", y = "Team Goals per game", title = "Variable may related to Goals per game") +
  theme_bw() +
  ggtitle("Variable may related to Goals per game") + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10, angle = 90, vjust = 0.5),
        strip.text = element_text(size = 10, face = "bold"))

# Save the plot
ggsave("data_plot/goals_linear.png", type = "cairo", dpi = 300, width = 6, height = 4, units = "in")
```






