# Where does the majority of the game happen
```{r}
library(shiny)
library(tidyverse)
library(readxl)

# Load the files into dataframes
  combined_pass <- read_excel("data_clean/combined_Pass.xlsx")
  combined_attack <- read_excel("data_clean/combined_attack.xlsx")

# Define UI
ui <- fluidPage(
  titlePanel("Passing and Attacking Statistics"),

  sidebarLayout(
    sidebarPanel(
      selectInput(inputId = "PassingAttackingTeam", 
                  label = "Select team:",
                  choices = c("Total",
                              sort(
                                unique(
                                  c(
                                    combined_pass$Team, combined_attack$Team)
                                  )
                                )
                              )
                  ),
      # No other inputs are needed in this example
    ),

    mainPanel(
      tabsetPanel(
        tabPanel("Passes", plotOutput("passPlot")),
        tabPanel("Attacks", plotOutput("attackPlot"))
      )
    )
  )
  
  
)


# Define server
server <- function(input, output) {

  

  # Define the reactive function for team selection
  selected_team <- reactive({
    if (input$PassingAttackingTeam == "Total") {
      list(pass_data = combined_pass %>%
             select(Touch_Defend, Touch_Middle, Touch_Attck) %>%
             rename("Defensive Third" = Touch_Defend,
                    "Middle Third" = Touch_Middle,
                    "Final Third" = Touch_Attck)%>%
             mutate_all(~.x / 32),
           
           
           attack_data = combined_attack %>%
             select(Attack_Left, Attack_middle, Attack_right) %>%
             rename("Left side" = Attack_Left,
                    "Middle side" = Attack_middle,
                    "Right side" = Attack_right)%>%
             mutate_all(~.x / 32))
    } else {
      list(pass_data = combined_pass %>%
             filter(Team == input$PassingAttackingTeam) %>%
             select(Touch_Defend, Touch_Middle, Touch_Attck) %>%
             rename("Defensive Third" = Touch_Defend,
                    "Middle Third" = Touch_Middle,
                    "Final Third" = Touch_Attck),
           attack_data = combined_attack %>%
             filter(Team == input$PassingAttackingTeam) %>%
             select(Attack_Left, Attack_middle, Attack_right) %>%
             rename("Left side" = Attack_Left,
                    "Middle side" = Attack_middle,
                    "Right side" = Attack_right))
    }
  })

  # Create a reactive function for plot title
  selected_team_title <- reactive({
    if (input$PassingAttackingTeam == "Total") {
      "Total Attacks pass average per game  by Location"
    } else {
      paste0(input$PassingAttackingTeam, " Total Attacks pass average per game  by Location")
    }
  })

  # Create a reactive bar chart for the pass data
  output$passPlot <- renderPlot({
    selected_team_data <- selected_team()
    
    pass_sum <- selected_team_data$pass_data %>% summarise(across(everything(), sum))
    pass_sum <- pass_sum %>% pivot_longer(cols = everything(), names_to = "Location", values_to = "Touches")

    pass_plot_title <- ifelse(input$PassingAttackingTeam == "Total",
                              "Total Passes average per game by Location",
                              paste0(input$PassingAttackingTeam, " Total Passes average per game by Location"))

    ggplot(pass_sum, aes(x = Location, y = Touches, fill = Location)) +
      geom_bar(stat = "identity") +
      labs(title = pass_plot_title, y = "Percentage of Total Passes", x = "Location") +
      scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
      scale_fill_brewer(palette = "Paired") +
      geom_label(aes(label = paste0(scales::percent(Touches), "\n")),
                 position = position_stack(vjust = 0.5),
                 color = "white")
  })

  # Create a reactive bar chart for the attack data
  output$attackPlot <- renderPlot({
    selected_team_data <- selected_team()

    attack_sum <- selected_team_data$attack_data %>% summarise(across(everything(), sum))
    attack_sum <- attack_sum %>% pivot_longer(cols = everything(), names_to = "Location", values_to = "Attacks")

    attack_plot_title <- ifelse(input$PassingAttackingTeam == "Total",
                                "Total Attacks pass average per game by Location",
                                paste0(input$PassingAttackingTeam, " Total Attacks pass average per game by Location"))

    ggplot(attack_sum, aes(x = Location, y = Attacks, fill = Location)) +
      geom_bar(stat = "identity") +
      labs(title = attack_plot_title, y = "Percentage of Total Attacks", x = "Location") +
      scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
      scale_fill_brewer(palette = "Paired") +
      geom_label(aes(label = paste0(scales::percent(Attacks), "\n")),
                 position = position_stack(vjust = 0.5),
                 color = "white")
  })

}



# Run the app
shinyApp(ui = ui, server = server)



```






#  Did teams who scored more goals have a higher chance of winning the tournament? 
```{r}
library(shiny)
library(openxlsx)
library(dplyr)
library(ggplot2)

# Define UI
ui <- fluidPage(

  # Application title
  titlePanel("Goals and Expected per game"),



    # Main panel
    mainPanel(
      plotOutput("goalsVsXgPlot", click = "plotClick"),
      verbatimTextOutput("clickedPoint")
    )

)

# Define server
server <- function(input, output) {

  # Read the team data
  team_data <- read.xlsx("data_clean/team_data.xlsx", sheet = 1)

  # Select team, games, goals per 90, and xg per 90 columns
  selected_cols <- team_data %>% select(team, games, goals_per90, xg_per90)

  # Filter the rows where games = 3, 4, 5, and 7
  filtered_data <- selected_cols %>%
    filter(games %in% c(3, 4, 5, 7))

  # Select the team, goals per 90, and xg per 90 columns
  plot_data <- filtered_data %>% select(team, games, goals_per90, xg_per90)

  # Create a plot of goals_per90 and xg_per90 for each team
  output$goalsVsXgPlot <- renderPlot({
    
    ggplot(plot_data, aes(x = goals_per90, y = xg_per90, label = team, col = as.factor(games))) + 
      geom_point(size = 3) + 
      geom_text(size = 3, nudge_x = 0.2, nudge_y = 0.2) +
      labs(x = "goals per game", y = "Expected goals per game", title = "Goals and Expected per game") +
      labs(col="Match")+
      scale_color_manual(values = c("#228B22", "#BDB76B", "#FF0000", "#0000FF"),
                         breaks = c(3, 4, 5, 7), 
                         labels = c("3 games", "4 games", "5 games", "7 games")) +
      theme_classic()
  })

  # Handle clicks on the plot
  output$clickedPoint <- renderPrint({
    click <- input$plotClick
    if (is.null(click)){
      return()
    }
    nearPointData <- nearPoints(plot_data, click, allRows = FALSE, maxpoints = 1)
    if (nrow(nearPointData) == 0) {
      return()
    }
    team <- unique(nearPointData$team)
    goals <- unique(nearPointData$goals_per90)
    xg <- unique(nearPointData$xg_per90)
    team_select <- unique(nearPointData$team)
    paste("Team: ", team, 
          ", Goals per game: ", goals, 
          ", Expected goals per game: ", xg)
  })


}

# Run the application
shinyApp(ui = ui, server = server)



```

#  which area is most dangerous for the defense?
# by angle
# by range


```{r}
library(openxlsx)
library(ggplot2)
library(shiny)

# Read data
attack_data <- read.xlsx("data_clean/combined_attack.xlsx", sheet = 1, startRow = 1)

# Define UI
ui <- fluidPage(
  

  # Application title
  titlePanel("Average Shots Taken by Team"),

  # Sidebar layout
  sidebarLayout(
    sidebarPanel(
      # Dropdown menu for team selection
      selectInput(inputId = "teamSelect", 
                  label = "Select team:",
                  choices = c("Average", unique(attack_data$Team)),
                  selected = "Average")
    ),
    
        # Main panel
    mainPanel(
      tabsetPanel(
        tabPanel("By Angle", plotOutput("shotAnglePlot")),
        tabPanel("By Location", plotOutput("shotRangePlot"))
      )
    )
  )
)


# Define server
server <- function(input, output) {
  
  
  
  # Create the plot by angle
  output$shotAnglePlot <- renderPlot({
    if (input$teamSelect == "Average") {
      avg_left_angle <- mean(attack_data$Shot_left)
      avg_middle_angle <- mean(attack_data$Shot_middle)
      avg_right_angle <- mean(attack_data$Shot_right)
    } else {
      team_data <- attack_data[attack_data$Team == input$teamSelect,]
      avg_left_angle <- mean(team_data$Shot_left)
      avg_middle_angle <- mean(team_data$Shot_middle)
      avg_right_angle <- mean(team_data$Shot_right)
    }
    
    
    # Create a data frame for plotting by angle
    avg_df_angle <- data.frame(location = c("Left", "Middle", "Right"), 
                           average = c(avg_left_angle, avg_middle_angle, avg_right_angle))
    
    
    ggplot(data = avg_df_angle, aes(x = location, y = average, fill = location)) +
      geom_bar(stat = "identity", color = "black", alpha = .8) +
      ggtitle(input$teamSelect," Team Average Shots Taken by Angle") +
      xlab("Shot Location") +
      ylab("Average Shots per game") +
      theme_minimal() +
      theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
            axis.title = element_text(size = 14, face = "bold"),
            axis.text = element_text(size = 12),
            legend.position = "none") +
      geom_text(aes(label = round(average, 2)), vjust = -0.5, size = 4)
  })
  
  
  
  # Create the plot by location
  output$shotRangePlot <- renderPlot({
    
    # Calculate average values by location
    if (input$teamSelect == "Average") {
      avg_left_location <- mean(attack_data$Shot_in_6_yard_box)
      avg_middle_location <- mean(attack_data$Shot_in_18_yard_box)
      avg_right_location <- mean(attack_data$Shot_outsie_box)
    } else {
      team_data <- attack_data[attack_data$Team == input$teamSelect,]
      avg_left_location <- mean(team_data$Shot_in_6_yard_box)
      avg_middle_location <- mean(team_data$Shot_in_18_yard_box)
      avg_right_location <- mean(team_data$Shot_outsie_box)
    }
    
    # Create a data frame for plotting by location
    avg_df_location <- data.frame(location = c("Goal", "Penalty", "Out of Box"), 
                               average = c(avg_left_location, avg_middle_location, avg_right_location))
    
    ggplot(data = avg_df_location, aes(x = location, y = average, fill = location)) +
      geom_bar(stat = "identity", color = "black", alpha = .8) +
      ggtitle(input$teamSelect,"Team Average Shots Taken by Location") +
      xlab("Shot Location") +
      ylab("Average Shots per game") +
      theme_minimal() +
      theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
            axis.title = element_text(size = 14, face = "bold"),
            axis.text = element_text(size = 12),
            legend.position = "none") +
      geom_text(aes(label = round(average, 2)), vjust = -0.5, size = 4)
  })
  
  
  
  
}




# Run the application
shinyApp(ui = ui, server = server)

```



# scatter plot and bar chart
```{r}
library(shiny)
library(openxlsx)
library(dplyr)
library(ggplot2)

attack_data <- read.xlsx("data_clean/combined_attack.xlsx", sheet = 1, startRow = 1)
# Read the team data
team_data <- read.xlsx("data_clean/team_data.xlsx", sheet = 1)
  
# Define UI
ui <- fluidPage(
  
  fluidRow(
    column(6,
           titlePanel("Goals and Expected per game")),
    column(6,
           titlePanel("Average Shots Taken by Team"))
  ),
  
  fluidRow(
    column(width = 6, plotOutput("goalsVsXgPlot", click = "plotClick"), verbatimTextOutput("clickedPoint")),
    
    column(width = 6, 
      tabsetPanel(
        tabPanel("By Angle", plotOutput("shotAnglePlot")),
        tabPanel("By Location", plotOutput("shotRangePlot"))
      )
    )
  ),



)

server <- function(input, output) {
  
  # Select team, games, goals per 90, and xg per 90 columns
  selected_cols <- team_data %>% select(team, games, goals_per90, xg_per90)

  # Filter the rows where games = 3, 4, 5, and 7
  filtered_data <- selected_cols %>%
    filter(games %in% c(3, 4, 5, 7))

  # Select the team, goals per 90, and xg per 90 columns
  plot_data <- filtered_data %>% select(team, games, goals_per90, xg_per90)

  # Create a plot of goals_per90 and xg_per90 for each team
  output$goalsVsXgPlot <- renderPlot({
    
    ggplot(plot_data, aes(x = goals_per90, y = xg_per90, label = team, col = as.factor(games))) + 
      geom_point(size = 3) + 
      geom_text(size = 3, nudge_x = 0.2, nudge_y = 0.2) +
      labs(x = "goals per game", y = "Expected goals per game", title = "Goals and Expected per game") +
      labs(col="Match")+
      scale_color_manual(values = c("#228B22", "#BDB76B", "#FF0000", "#0000FF"),
                         breaks = c(3, 4, 5, 7), 
                         labels = c("3 games", "4 games", "5 games", "7 games")) +
      theme_classic()
  })

  # Handle clicks on the plot
  
  # Define reactive variable to store team selection
  teamSelect <- reactiveVal()
  
  output$clickedPoint <- renderPrint({
    click <- input$plotClick
    if (is.null(click)){
      return()
    }
    nearPointData <- nearPoints(plot_data, click, allRows = FALSE, maxpoints = 1)
    if (nrow(nearPointData) == 0) {
      return()
    }
    team <- unique(nearPointData$team)
    goals <- unique(nearPointData$goals_per90)
    xg <- unique(nearPointData$xg_per90)
    #teamSelect <- unique(nearPointData$team)
    teamSelect(unique(nearPointData$team))
    paste("Team: ", team, 
          ", Goals per game: ", goals, 
          ", Expected goals per game: ", xg)
  })
  
  
  
  
  # Create the plot by angle
  output$shotAnglePlot <- renderPlot({
    
    # Get the selected team
    teamSelect <- ifelse(is.null(teamSelect()), "Average", teamSelect())
    
    #if (input$teamSelect == "Average")
    if (teamSelect == "Average") {
      avg_left_angle <- mean(attack_data$Shot_left)
      avg_middle_angle <- mean(attack_data$Shot_middle)
      avg_right_angle <- mean(attack_data$Shot_right)
    } else {
      team_data <- attack_data[attack_data$Team == teamSelect,]
      avg_left_angle <- mean(team_data$Shot_left)
      avg_middle_angle <- mean(team_data$Shot_middle)
      avg_right_angle <- mean(team_data$Shot_right)
    }
    
    
    # Create a data frame for plotting by angle
    avg_df_angle <- data.frame(location = c("Left", "Middle", "Right"), 
                           average = c(avg_left_angle, avg_middle_angle, avg_right_angle))
    
    
    ggplot(data = avg_df_angle, aes(x = location, y = average, fill = location)) +
      geom_bar(stat = "identity", color = "black", alpha = .8) +
      ggtitle(teamSelect," Team Average Shots Taken by Angle") +
      xlab("Shot Location") +
      ylab("Average Shots per game") +
      theme_minimal() +
      theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
            axis.title = element_text(size = 14, face = "bold"),
            axis.text = element_text(size = 12),
            legend.position = "none") +
      geom_text(aes(label = round(average, 2)), vjust = -0.5, size = 4)
  })
  
  
  
  # Create the plot by location
  output$shotRangePlot <- renderPlot({
    
    # Get the selected team
    teamSelect <- ifelse(is.null(teamSelect()), "Average", teamSelect())
    
    # Calculate average values by location
    # if (input$teamSelect == "Average") 
    if (teamSelect == "Average") {
      avg_left_location <- mean(attack_data$Shot_in_6_yard_box)
      avg_middle_location <- mean(attack_data$Shot_in_18_yard_box)
      avg_right_location <- mean(attack_data$Shot_outsie_box)
    } else {
      team_data <- attack_data[attack_data$Team == teamSelect,]
      avg_left_location <- mean(team_data$Shot_in_6_yard_box)
      avg_middle_location <- mean(team_data$Shot_in_18_yard_box)
      avg_right_location <- mean(team_data$Shot_outsie_box)
    }
    
    # Create a data frame for plotting by location
    avg_df_location <- data.frame(location = c("Goal", "Penalty", "Out of Box"), 
                               average = c(avg_left_location, avg_middle_location, avg_right_location))
    
    ggplot(data = avg_df_location, aes(x = location, y = average, fill = location)) +
      geom_bar(stat = "identity", color = "black", alpha = .8) +
      ggtitle(teamSelect,"Team Average Shots Taken by Location") +
      xlab("Shot Location") +
      ylab("Average Shots per game") +
      theme_minimal() +
      theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
            axis.title = element_text(size = 14, face = "bold"),
            axis.text = element_text(size = 12),
            legend.position = "none") +
      geom_text(aes(label = round(average, 2)), vjust = -0.5, size = 4)
  })


  
  
}

# Run the application
shinyApp(ui = ui, server = server)
```



# from Defend
# search all columns from combined_Defend.xlsx in Croatia row. compare the value with the average. put the value larger than average in positive and lower than average value columns in negative.
```{r}

library(shiny)
library(openxlsx)
library(ggplot2)
library(ggrepel)
library(plotly)

# Read data for Combined Attack
combined_Defend <- read.xlsx("data_clean/combined_Defend.xlsx", sheet = 1, startRow = 1)

# Define UI for application
ui <- fluidPage(

  fluidRow(
    column(8, align = "center", h1("Defend Statistics as Radar Plot")),
    column(4, align = "right", selectInput("radar_team", "Select a team:",
                                           choices = unique(combined_Defend$Team)))
  ),
  
  hr(),
  
  # Show a plot of the selected team's defend statistics
  fluidRow(
    column(6, plotlyOutput("defend_radar_plot"))
  )
  
  
)

# Define server logic
server <- function(input, output) {
  
  # Create a reactive plot based on the selected team
  output$defend_radar_plot <- renderPlotly({
    # Find selected team's row
    choice_team_row <- combined_Defend[combined_Defend$Team == input$radar_team, ][, -1]
    
    # Calculate the average statistic values across all teams
    avg_stats <- colMeans(combined_Defend[, -1])
    
    team_row <- (choice_team_row - avg_stats) * 100 / avg_stats
    
    # Create a data frame for plotting
    diff_df <- data.frame(statistic = colnames(team_row),
                          value = as.numeric(team_row),
                          stringsAsFactors = FALSE)
    
    # Create the plot
    plot_ly(diff_df, type = "scatterpolar", mode = "lines", line = list(width = 2, color = '#636EFA')) %>%
      add_trace(r = diff_df$value, theta = diff_df$statistic,
                name = paste0(input$radar_team, "'s Defend Statistics")) %>%
      layout(
        title = paste0(input$radar_team, "'s Defend Statistics"),
        polar = list(radialaxis = list(visible = TRUE, range = c(-50, 80))),
        showlegend = TRUE,
        legend = list(
          x = 0.1, y = 0.9,
          bgcolor = "rgba(255, 255, 255, 0.85)",
          bordercolor = "#FFFFFF",
          borderwidth = 2
        ),
        margin = list(l = 20, r = 20, b = 20, t = 40),
        paper_bgcolor = "white",
        plot_bgcolor = "white"
      )
  })
  
}

# Run the application
shinyApp(ui, server)


```




# for the pass
```{r}


library(shiny)
library(openxlsx)
library(ggplot2)
library(ggrepel)
library(plotly)

# Read data for Combined Attack
combined_Pass <- read.xlsx("data_clean/combined_Pass.xlsx", sheet = 1, startRow = 1)

# Define UI for application
ui <- fluidPage(
  
  fluidRow(
    column(6, align = "center", h1("Pass Statistics Plot")),
    column(4, align = "right", selectInput("radar_team", "Select a team:",
                                           choices = unique(combined_Pass$Team)))
  ),
  
  hr(),
  
  # Show a plot of the selected team's defend statistics
  fluidRow(
    column(6, plotlyOutput("pass_radar_plot"))
  )
  
  
)

# Define server logic
server <- function(input, output) {
  
  # Create a reactive plot based on the selected team
  output$pass_radar_plot <- renderPlotly({
    # Find selected team's row
    choice_team_row <- combined_Pass[combined_Pass$Team == input$radar_team, ][, -1]
    
    # Calculate the average statistic values across all teams
    avg_stats <- colMeans(combined_Pass[, -1])
    
    team_row <- (choice_team_row - avg_stats) * 100 / avg_stats
    
    # Create a data frame for plotting
    diff_df <- data.frame(statistic = colnames(team_row),
                          value = as.numeric(team_row),
                          stringsAsFactors = FALSE)
    
    # Create the plot
    plot_ly(diff_df, type = "scatterpolar", mode = "lines", line = list(width = 2, color = '#636EFA')) %>%
      add_trace(r = diff_df$value, theta = diff_df$statistic,
                name = paste0(input$radar_team, "'s Defend Statistics")) %>%
      layout(
        title = paste0(input$radar_team, "'s Defend Statistics"),
        polar = list(radialaxis = list(visible = TRUE, range = c(-50, 50))),
        showlegend = TRUE,
        legend = list(
          x = 0.1, y = 0.9,
          bgcolor = "rgba(255, 255, 255, 0.85)",
          bordercolor = "#FFFFFF",
          borderwidth = 2
        ),
        margin = list(l = 20, r = 20, b = 20, t = 40),
        paper_bgcolor = "white",
        plot_bgcolor = "white"
      )
  })
  
}

# Run the application
shinyApp(ui, server)


```





# combine two radar map together
```{r}
library(shiny)
library(openxlsx)
library(ggplot2)
library(ggrepel)
library(plotly)

# Read data for Combined Attack
combined_Defend <- read.xlsx("data_clean/combined_Defend.xlsx", sheet = 1, startRow = 1)
# Read data for combined_Pass
combined_Pass <- read.xlsx("data_clean/combined_Pass.xlsx", sheet = 1, startRow = 1)

# Define UI for application
ui <- fluidPage(

  fluidRow(
    column(8, align = "center", h1("Team statistics compare average as Radar Plot")),
    column(4, align = "right", selectInput("radar_team", "Select a team:",
                                           choices = unique(combined_Defend$Team)))
  ),
  
  fluidRow(
    column(6, align = "center", h1("Defend Statistics Plot")),
    column(6, align = "center", h1("Pass Statistics Plot")),
    
  ),
  
  hr(),
  
  hr(),
  
  # Show a plot of the selected team's defend statistics
  fluidRow(
    column(6, plotlyOutput("defend_radar_plot")),
    column(6, plotlyOutput("pass_radar_plot")),
  )
  
  
)

# Define server logic
server <- function(input, output) {
  
  # Create a reactive plot based on the selected team
  output$defend_radar_plot <- renderPlotly({
    # Find selected team's row
    choice_team_row <- combined_Defend[combined_Defend$Team == input$radar_team, ][, -1]
    
    # Calculate the average statistic values across all teams
    avg_stats <- colMeans(combined_Defend[, -1])
    
    team_row <- (choice_team_row - avg_stats) * 100 / avg_stats
    
    # Create a data frame for plotting
    diff_df <- data.frame(statistic = colnames(team_row),
                          value = as.numeric(team_row),
                          stringsAsFactors = FALSE)
    
    # Create the plot
    plot_ly(diff_df, type = "scatterpolar", mode = "lines", line = list(width = 2, color = '#636EFA')) %>%
      add_trace(r = diff_df$value, theta = diff_df$statistic,
                name = paste0(input$radar_team, "'s Defend Statistics")) %>%
      layout(
        title = paste0(input$radar_team, "'s Defend Statistics"),
        polar = list(radialaxis = list(visible = TRUE, range = c(-50, 80))),
        showlegend = TRUE,
        legend = list(
          x = 0.1, y = 0.9,
          bgcolor = "rgba(255, 255, 255, 0.85)",
          bordercolor = "#FFFFFF",
          borderwidth = 2
        ),
        margin = list(l = 20, r = 20, b = 20, t = 40),
        paper_bgcolor = "white",
        plot_bgcolor = "white"
      )
  })
   
    # Create a reactive plot based on the selected team
  output$pass_radar_plot <- renderPlotly({
    # Find selected team's row
    choice_team_row <- combined_Pass[combined_Pass$Team == input$radar_team, ][, -1]
    
    # Calculate the average statistic values across all teams
    avg_stats <- colMeans(combined_Pass[, -1])
    
    team_row <- (choice_team_row - avg_stats) * 100 / avg_stats
    
    # Create a data frame for plotting
    diff_df <- data.frame(statistic = colnames(team_row),
                          value = as.numeric(team_row),
                          stringsAsFactors = FALSE)
    
    # Create the plot
    plot_ly(diff_df, type = "scatterpolar", mode = "lines", line = list(width = 2, color = '#636EFA')) %>%
      add_trace(r = diff_df$value, theta = diff_df$statistic,
                name = paste0(input$radar_team, "'s Defend Statistics")) %>%
      layout(
        title = paste0(input$radar_team, "'s Defend Statistics"),
        polar = list(radialaxis = list(visible = TRUE, range = c(-50, 50))),
        showlegend = TRUE,
        legend = list(
          x = 0.1, y = 0.9,
          bgcolor = "rgba(255, 255, 255, 0.85)",
          bordercolor = "#FFFFFF",
          borderwidth = 2
        ),
        margin = list(l = 20, r = 20, b = 20, t = 40),
        paper_bgcolor = "white",
        plot_bgcolor = "white"
      )
  })

}

# Run the application
shinyApp(ui, server)
```







